\chapter{Project Requirements}
\label{ch:requirements}

This chapter outlines the functional and non-functional requirements for the ORICALO Urdu-Native Voice Agent.

\section{Core Use Cases}

\textbf{1. Inbound Property Inquiry Call}: A customer initiates a voice session. The system transcribes the Urdu speech, retrieves relevant property listings (RAG) and price estimates (AVM), and synthesizes a natural Urdu response. The conversation state is maintained, and upon completion, the transcript is saved, PII is redacted, and the lead is scored in the CRM.

\textbf{2. Outbound Lead Qualification}: An agent triggers a call from the CRM dashboard. Twilio routes the call to the ORICALO Voice Orchestrator, which conducts an autonomous qualification conversation, extracting budget and timeline, and updating the CRM status automatically.

\textbf{3. Property Price Estimation}: A user requests a valuation. The system normalizes the area metric (Marla to SqFt) based on society standards (e.g., DHA vs. standard) and utilizes an ML-model or heuristic fallback to return a predicted price range.

\textbf{4. Post-Call Analytics}: Following any call, the system asynchronously extracts intent, redacts sensitive information (CNIC, phone numbers), calculates a 0--100 lead score using an LLM, and creates actionable tasks for human supervisors if the lead is ``Hot''.

\section{Functional Requirements (FR)}

\begin{itemize}
    \item \textbf{ASR \& TTS}: Stream Urdu transcription with $<20\%$ WER and synthesize responses with low-latency barge-in support.
    \item \textbf{Dialogue \& RAG}: Maintain multi-turn context, extract location entities, and ground responses using ChromaDB top-$K$ semantic search.
    \item \textbf{Orchestrator}: Maintain a LISTENING $\rightarrow$ PROCESSING $\rightarrow$ SPEAKING state machine that instantly cancels tasks on user interruption.
    \item \textbf{CRM \& Analytics}: Persist all interactions in PostgreSQL, redact PII with $>95\%$ recall, and manage automated follow-ups.
\end{itemize}

\section{Non-Functional Requirements (NFR)}

\begin{itemize}
    \item \textbf{Performance}: Deliver the first TTS audio chunk within 1s of LLM sentence completion, and AVM API response under 500ms.
    \item \textbf{Reliability}: Graceful degradation to SQLite if PostgreSQL fails, and robust WebSocket cleanup during barge-in events.
    \item \textbf{Security}: Exclusive use of environment variables for API keys and regex-based PII scrubbing before database persistence.
\end{itemize}
