\documentclass{fast-nuces-bs}

\usepackage{blindtext}
\usepackage{mathptmx}% Times Roman font
\usepackage[T1]{fontenc}
\usepackage{lipsum} 
\usepackage{sectsty}
\usepackage{tikz-uml}
\usepackage{titlesec}
\usepackage{listings}
\usepackage{xcolor}

% Code listing style
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{blue},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2,
    frame=single,
    extendedchars=true,
    literate={♪}{{$\sharp$}}1
}

\lstset{style=mystyle}

% Information about the Thesis 
% -----------------------------------------------------------------------------
% (All are compulsory, do not delete any line other than author Information)
% For e.g., usually there are 3 students in a group, so leave authorone, 
% authortwo, and authorthree, and delete authorfour.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\department{Department of Software Engineering}
\faculty{Software Engineering}
\degreeyear{2026}
\degreemonth{December}
\degreename{Software Engineering}
\campuscity{Islamabad}
\authorone{Abdul Rafay}{22I-8762}
\authortwo{Sumeed Jawad Kanwar}{22I-2651}
\authorthree{Huzaifa Mahmood}{22I-2669}
\supervisor{Mr. Ahmed Raza Shahid}
\sessionduration{2022-2026}
\deanname{Dr. Dean Computing}
\directorname{Dr. Director of the Campus}
\hodname{Dr. Head of Software Engineering Department}
%\fypcoordinatorname{Name of FYP Coordinator}
\title{Urdu-Native Voice Agent for Real Estate Marketing in Pakistan}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Former document starts below this
\begin{document}

% Abstract (as a chapter instead of environment)
\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}

The real estate sector in Pakistan relies heavily on voice-based communication conducted primarily in Urdu and Roman Urdu. Current AI voice solutions are predominantly optimized for English, resulting in poor performance in transcription accuracy, dialogue management, and speech synthesis for local languages. This project addresses the critical gap by developing an open-source, locally deployable Urdu-Native Voice Agent that automates real estate lead generation and customer inquiry handling.

This report presents the Iteration 2 deliverables, building upon the ASR foundation established in Iteration 1 to integrate LLM-based dialogue management, Retrieval-Augmented Generation (RAG) for property data grounding, and price prediction capabilities. The system now provides an end-to-end voice AI pipeline from audio input through intelligent response generation with interactive UI widgets.

% Main Chapters
\include{sections/chapter1}
\include{sections/chapter2}
\include{sections/chapter3}
\include{sections/chapter4}
\include{sections/chapter5}
\include{sections/chapter6}
\include{sections/conclusions}

% Appendix
\include{sections/appendix1}

% Bibliography
\bibliographystyle{plain}
% \bibliography{bib}
\addcontentsline{toc}{chapter}{References}

\end{document}
